### 2024-04-03 texts/paper_closing.tex
add artfacts size (quantiles), yeet PCA remainders

% Created 2024-03-20 wo 16:51
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

Secondly, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
Partial maximum likelihood allows estimation of \(\beta\) without defining the baseline hazard rate, which is therefore not constrained to a parametric form. 
Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Mar  6 21:27:16 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 276 & 0.575 &  0.592 &  0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.158 &  0.168 &  0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &  0.240 &  0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &  0.093 &  0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 179 & 0.373 &  0.408 &  0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.210 &  0.191 &  0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &  0.141 &  0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.477 &  0.487 &  0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &  0.296 &  0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &  0.794 &  0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &  0.149 &  0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 & 1 \\ 
   & PC1 (Size) &  &  &  0.344 &  4.26 & -6.2 & 13.90 \\ 
   & PC2 (Support) &  &  & -0.046 &  1.99 & -5.6 & 6.70 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
   & Pop. (millions) within 10km &  &  &  1.382 &  1.74 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  &  2.681 &  2.97 & 1 & 16 \\ 
   & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &  0.281 &  0.45 & 0 & 1 \\ 
   & Region - Europe & 242 & 0.504 &  0.502 &  0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &  0.144 &  0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Mar  6 21:27:26 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .42 \; (0.37) \\ 
   & Gender - Couple & .66 \; (0.38) \\ 
   & Founder died & 1.33 \; (0.55)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .94 \; (0.50) \\ 
   & Self-Identification - Collection & .07 \; (0.60) \\ 
   & Self-Identification - Other & 1.16 \; (0.39)^{**} \\ 
   & AN Ranking - Included & .33 \; (0.43) \\ 
   & AN Ranking - Dropped & 1.26 \; (0.49)^{*} \\ 
   & Founder name in Museum name & -.57 \; (0.33) \\ 
   & MOW inclusion & -.28 \; (0.41) \\ 
   & PC1 (Size) & -.34 \; (0.06)^{***} \\ 
   & PC2 (Support) & -.11 \; (0.11) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.05 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   & Pop. (millions) within 10km & .00 \; (0.11) \\ 
   & Nbr PM within 10km & .13 \; (0.06)^{*} \\ 
   \hline
 & Museum-years & 6903 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -236.48 \\ 
   & AIC & 504.96 \\ 
   & BIC & 536.48 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

>>>>

% Created 2024-04-03 wo 13:56
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

Secondly, we use Cox proportional hazard models which estimate the relationship between covariates and the hazard rate.
The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form. 
Coefficients are interpeted as log hazard ratios, i.e. as multipliers of the baseline hazard rate.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 13:38:27 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 276 & 0.575 &  0.592 &  0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.158 &  0.168 &  0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &  0.240 &  0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &  0.093 &  0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 179 & 0.373 &  0.408 &  0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.210 &  0.191 &  0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &  0.141 &  0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.477 &  0.487 &  0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &  0.296 &  0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &  0.794 &  0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &  0.149 &  0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &  0.057 &  0.23 & 0 & 1 \\ 
   & Exhibition Quantile &  &  &  0.428 &  0.24 & 0.083 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density &  &  & 20.541 & 18.37 & 1 & 62 \\ 
   & Pop. (millions) within 10km &  &  &  1.382 &  1.74 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  &  2.681 &  2.97 & 1 & 16 \\ 
   & Europe and North America & 313 & 0.652 &  0.645 &  0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &  0.281 &  0.45 & 0 & 1 \\ 
   & Region - Europe & 242 & 0.504 &  0.502 &  0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &  0.144 &  0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 13:14:43 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more} & \multicolumn{1}{l}{r\_waf}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .19 \; (0.36) & .52 \; (0.47) \\ 
   & Gender - Couple & .08 \; (0.36) & .24 \; (0.44) \\ 
   & Founder died & .11 \; (0.53) & -.09 \; (0.69) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .81 \; (0.48) & 1.01 \; (0.67) \\ 
   & Self-Identification - Collection & .45 \; (0.58) & .85 \; (0.73) \\ 
   & Self-Identification - Other & 1.29 \; (0.38)^{***} & 1.40 \; (0.56)^{*} \\ 
   & AN Ranking - Included & .38 \; (0.41) & .38 \; (0.51) \\ 
   & AN Ranking - Dropped & 1.15 \; (0.45)^{*} & 1.31 \; (0.62)^{*} \\ 
   & Founder name in Museum name & -.31 \; (0.33) & -.35 \; (0.41) \\ 
   & MOW inclusion & -.81 \; (0.40)^{*} & -.66 \; (0.51) \\ 
   & Exhibition Quantile &  & -.70 \; (0.82) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & PM density & -.05 \; (0.03) & -.02 \; (0.04) \\ 
   & PM density$^{2}$ & .00 \; (0.00) & .00 \; (0.00) \\ 
   & Pop. (millions) within 10km & .02 \; (0.11) & .10 \; (0.12) \\ 
   & Nbr PM within 10km & .11 \; (0.06)^{*} & .07 \; (0.09) \\ 
   \hline
 & Museum-years & 6903 & 3292 \\ 
   & Closures & 53 & 33 \\ 
   & log. Likelihood & -263.16 & -137.85 \\ 
   & AIC & 554.31 & 305.71 \\ 
   & BIC & 581.90 & 328.16 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}
